Global patterns of forest autotrophic carbon fluxes

### 2020-12-17 manuscript/response to reviews.Rmd

**Most of the points raised here are covered by more specific comments below, and our responses to these points follow those comments.**

**We believe that one general problem may have been that the previous manuscript version didn't clearly communicate our intentions, which were not to pose novel hypotheses but to conduct a quantitative review of the subject using a vastly expanded and standardized dataset. While we feel that the text of the introduction made it clear that we weren't intending to present the hypotheses as novel, we have realized that a quick review of Table 1 in isolation would give the false impression that we intended these analyses as novel hypothesis tests. We have taken some steps to improve this aspect:**

**1. We modified Table 1, labeling the questions as "review questions" and clarifying that many of the hypotheses have been previously tested, citing relevant publications.**

**2. We have made the following revisions to the language in the abstract and introduction to clarify that our intention is to provide a quantitative review that clarifies uncertainty in these relationships:**

@@

- **Abstract: "Here, we draw upon 1,319 records from the Global Forest Carbon Database (ForC), representing all major forest types and the nine most significant autotrophic carbon fluxes, to comprehensively ~~explore~~ *review* how annual C cycling in mature, undisturbed forests varies with latitude and climate on a global scale."** 
- **Introduction: "In order to approach this broad topic, we simplify the major gaps in our knowledge to five broad *review questions* and corresponding predictions (Table 1)."**

**One point above that is not addressed below is that we present "simple statistical analyses". While we concur that the analyses are relatively simple, that does not preclude their being appropriate, informative, and sufficient. They represent several substantive advances over past analyses of this type:**

-  **They are underlain by a large, standardized database that accounts for factors such as stand age and management, which have not always been accounted for.**

-  **We use mixed effects model to account for random effects of location (plot nested within geographic area), thereby accounting for potential pseudoreplication, which has not always been done in the past.**

-  **We examined nine carbon fluxes and relationships among them--more than has been concurrently analyzed in the past.**

-  **For each flux variable, we tested a wide range of models: univariate responses to 12 climate variables (3 functional fit types for each), along with multivariate models (MAT x MAP for all, along with other combinations not presented).**

@@

**Thus, although the analyses are simple, we believe them to be appropriate and sufficient, with their novelty arising not from the analysis method itself but from the coverage and extent of the dataset.**

The analyses performed were too conventional that similar analyses with a smaller size of similar datasets have been performed a decade ago.

**This statement suggests a lack of perspective on the scope of our analysis relative to previous studies. Whereas most studies consider at most a few flux variables, ours considers nine. The most comprehensive similar study is @luyssaert_co_2007, which was published in *GCB* more than a decade ago, was based on a database <25% the size of the ForC version used here, did not control for effects of stand age/ disturbance history, and examined latitudinal/ global climatic trends in only three variables. Thus, the current analysis will be at the clear forefront of studies examining correlations between forest carbon flux and climate at the global scale.**

**To help clarify the scope of this analysis to readers, we added the following statement to the last paragraph of the introduction: "Our analyses represent a major step forward in relation to previous work [e.g., @luyssaert_co_2007] in that we examine global climatic trends in more variables (9 vs. $\le$ 3), draw from a much larger database (>4 times more records analyzed), and control for the effects of stand age, disturbance, and management."**

**We note in particular that in @luyssaert_co_2007, mean stand age was extremely variable across biomes, and while mean stand age in tropical forests was >100 years (old growth) in all but one extra-tropical biome, mean stand age was <100. This is likely to elevate productivity estimates for extra-tropical biomes, highlighting the need for a comprehensive, standardised dataset for analysis.**

### 2020-12-17 manuscript/manuscript draft.Rmd
working on resonse to reviews

The recent development of the Global Forest Carbon database (ForC), which synthesizes multiple variables and includes records of stand history [@anderson-teixeira_carbon_2016; @anderson-teixeira_forc_2018], opens up the possibility for a standardized analysis of global scale variation in multiple C fluxes and the principle climatic drivers of these patterns.
In order to approach this broad topic, we simplify the major gaps in our knowledge to five broad review questions and corresponding predictions (Table 1).
First, we ask how nine forest autotrophic carbon fluxes in ForC vary with latitude (*Q1*).
We then test how these fluxes relate to $MAT$ and $MAP$ (*Q2*), and additionally how they respond to other, less well-studied, climate variables (*Q3*).
Finally, we consider the relationship between C flux and seasonality, considering the role of seasonality in explaining variation in carbon fluxes (*Q4*), and the influence of climate on C flux standardized by growing season length (*Q5*).
Our analyses represent a major step forward in relation to previous work [@luyssaert_co_2007] in that we examine global climatic trends in more variables (9 vs. $\le$ 3), draw from a much larger database (>4 times more records analyzed), and control for the effects of stand age, disturbance, and management (not consistenly done previously).

>>>>

The recent development of the Global Forest Carbon database (ForC), which synthesizes multiple variables and includes records of stand history [@anderson-teixeira_carbon_2016; @anderson-teixeira_forc_2018], opens up the possibility for a standardized analysis of global scale variation in multiple C fluxes and the principle climatic drivers of these patterns.
In order to approach this broad topic, we simplify the major gaps in our knowledge to five broad review questions and corresponding predictions (Table 1).
First, we ask how nine forest autotrophic carbon fluxes in ForC vary with latitude (*Q1*).
We then test how these fluxes relate to $MAT$ and $MAP$ (*Q2*), and additionally how they respond to other, less well-studied, climate variables (*Q3*).
Finally, we consider the relationship between C flux and seasonality, considering the role of seasonality in explaining variation in carbon fluxes (*Q4*), and the influence of climate on C flux standardized by growing season length (*Q5*).
Our analyses represent a major step forward in relation to previous work [e.g., @luyssaert_co_2007] in that we examine global climatic trends in more variables (9 vs. $\le$ 3), draw from a much larger database (>4 times more records analyzed), and control for the effects of stand age, disturbance, and management.
